---
title: "Machine Learning Model"
output: html_document
params:
  outDir: "."
  traindat: traindat
  target: target
  rseed: NA
---


  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=FALSE,
                      warning = FALSE, message = FALSE,
                      results = 'show',
                      eval = TRUE)  ## flag eval = false for quick text edits
```

```{r, echo=FALSE}
# install.packages("mlr", dependencies = TRUE)
library(mlr)
library(tidyverse)

## Load the data
modDat <- params$traindat
target <- params$target
          
## define output directory
outDir <- params$outDir
```

<!-- # _Testing_  -->
<!-- ```{r} -->
<!-- ## Load the data -->
<!-- modDat <- sf::st_read("e:/workspace/2020/PEM/ALRF_PEMv2/spatialData/SamplePoints_with_rast_values.gpkg", -->
<!--   quiet = TRUE) %>%  -->
<!--   dplyr::select(SiteSeries, aspect_025:VerticalDistance_25m) %>%  -->
<!--   dplyr::select(-c(Vertical_distance_025:VerticalDistance_25m,   ## remove problematic covariates -->
<!--                    overland_flow_025:OverlandFlowDistance_25m)) %>%  -->
<!--   as.data.frame() -->
<!-- modDat <- modDat[, -length(modDat)] -->
<!-- modDat <- modDat[!is.na(modDat$SiteSeries),] -->
<!-- target <- "SiteSeries" -->

<!-- ## define output directory -->
<!-- outDir <- "e:/tmp/mlr_5m_200323/" -->
<!-- rseed <- NA -->
<!-- ``` -->





## Response variable: _`r target`_

These are the response variable classes including the number in each class that we want to predict. 
```{r,echo=FALSE}
table(modDat[, target])
```


## Begin modeling 


### Define the Task and Learner

_PERHAPS -- this should be another small function or sourced other options_ 

```{r, echo=FALSE}
## use or create a random number seed -- this can be used to repeat results in future.
if (!is.na(rseed)) {
  set.seed(rseed) 
  print(paste("Random number generator seed set to:", rseed))
  } else {
  rseed <- as.integer(Sys.time())
  print(paste("Random number generator seed set to:", rseed))
} 


```

```{r}
## Create task 
tsk <- makeClassifTask(data = modDat, target = "SiteSeries")

## Define Learner
lrn <- makeLearner("classif.ranger",
                   num.trees = 500,                         ## number of trees DEFAULT: 500
                   mtry = round(sqrt(ncol(modDat)-1)),      ## someone showed me to declare mtry this way
                   num.threads = parallel::detectCores()*2, ## CAUTION HERE: how many threads does your machine have?
                   importance = "impurity",                 ## collect var importance data
                   predict.type = "prob")                   ## model will generate prob. and multi-class
```

### Complete repeated cross-fold validataion

_PERHAPS -- this should be another small function or sourced other options_ 

```{r}
## Defines the validation method
resp <- makeResampleDesc("RepCV",     ## repeated cross fold
                         folds = 10,   ## k-folds 5 or 10 as default.  Ideally all folds should be equal size.
                         reps  = 3)   ## note this will mean 5 x 3 iterations through the data
   ## note: 5 fold 3 repeats is a little low.  I would prefer 10 x 10 but that takes additional time...

## Execute cross validation
cv <- mlr::resample(learner = lrn,
               task = tsk,
               resampling = resp)

saveRDS(cv, file = paste(outDir, "cv_results.rds", sep = "/"))
```

#### Resampling results

The mean mis-classification error is **`r mean(cv$measures.test$mmce)`**.


#### Confusion Matrices 

```{r}
cf_matrix <- calculateConfusionMatrix(cv$pred,
                                      relative = TRUE,
                                      sums = TRUE)
```

##### Absolute matrix

<div style = "font-size:10pt">

```{r cf-matix, echo = FALSE}
knitr::kable(cf_matrix$result)
```

</div>


##### Relative Matrix

<div style = "font-size:10pt">

```{r cf-matix-rel, echo=FALSE}
knitr::kable(round(cf_matrix$relative.row, 2))
```

</div>


### Train the model

The model is trained using all the data and then saved. 
```{r}
mod <- train(lrn, tsk)

saveRDS(mod, paste(outDir, "model.rds", sep = "/"))
```

### Variable importance

```{r var-imp, echo=FALSE}
var_imp <- as.data.frame(mod$learner.model$variable.importance) %>%
    rownames_to_column()
  names(var_imp) <- c("name", "VaribleImportance")

knitr::kable(var_imp %>% arrange(desc(VaribleImportance)) %>% head(., 20))
```


## Complete

Congratulations your model has been generated. 

Files are saved: 

```{r, echo = FALSE}
# outDir <- "e:/tmp/model_gen_test/" ## Testing
fn <- as.data.frame(list.files(outDir, full.names = TRUE))
names(fn) <- "Files"
knitr::kable(fn)
```


