---
title: "Machine Learning Model: using ranger via the tidyverse"
output: html_document
params:
  outDir:  "."
  trDat:   trDat
  target:  target
  target2: target2
  covars:  covars
  tid:     tid
  slice:   slice
  rseed:   NA
  infiles: infiles
  mmu:     mmu
  mname:   mname
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=FALSE,
                      warning = FALSE, message = FALSE,
                      results = 'hold',
                      eval = TRUE)  ## flag eval = false for quick text edits
```


```{r, echo=FALSE}
## Load the data and parameters as specified in the R script (model_gen_tidy.R)
## A challenge for moving this to a function is having the variables listed in this chunk 
##    also listed within the dataframe -- problematic for running the model

outDir  <- params$outDir    # where the model will be saved
trDat   <- params$trDat     # Training data 
target  <- params$target    # primary call or target column name
target2 <- params$target2   # secondary call or second target
bgc     <- params$bgc       
covars  <- params$covars    # character vector of covariates 
groupid <- params$tid       # Transect ID
slice   <- params$slice     # identify the slice that will be used 
infiles <- params$infiles   # ?? 
mmu     <- params$mmu       # Text -- which level are you mapping 
mname   <- params$mname     # Name of the model
rseed   <- params$rseed     # random seed 
# field_transect <- params$field_transect  # GP -- no longer needed ... was for AA.

```


```{r}
library(data.table)
library(knitr)
library(cowplot)
library(tidymodels)
library(tidyverse)
library(themis)
library(ggplot2)
library(janitor)
library(sf) ## needed?
```



```{r}

#
# # Manual testing : option
# #
# #trDat = mpts          # load all bgc model data
    inmdata_all <- st_read("f:/PEM_Methods_Research/Deception_AOI/1_map_inputs/trainingData/att_5m/s1_deception_pts_att.gpkg") %>% 
      as_tibble()
    trDat = inmdata_all   # load per bgc model data
# # # # # #
    target = "mapunit1"       # primary call or target column name
    target2 = "mapunit1"      # 
     names(trDat)                     ## 
     covars <- names(trDat[,10:130])  ## manually set covars list  
    bgc <- "bgc"
    groupid = "transect_id"             # how the data is grouped for cross validation 
    slice = "slice"
    outDir = "d:/tmp"         # output file
    indata = "f:/PEM_Methods_Research/Deception_AOI/1_map_inputs/trainingData/att_5m/s1_deception_pts_att.gpkg"         # name of input data file for reporting
    rseed = 456             # define seed to remove random nature of model
    mmu = "mmu"               #
    mname = "Test using Deception"           # model name for reporting
     
     
    

```


This model uses the following parameters:

* **model reference:** `r mname`
* **mapunit:** `r mmu`
* **training point set : **`r infiles`
* **model response and covariates: ** `r names(trDat)`


## Response variable: _`r target`_

The following training points and frequency of points were used in the model.

```{r summary, echo = FALSE, include = TRUE, fig.asp=1.2}
table(trDat[, target])

# calculate summary of raw training data set -- currently not in use? 
trDat_sum <- trDat %>%
  dplyr::group_by_at(target) %>%
  dplyr::summarise(freq = n()) %>%
  dplyr::mutate(prop = round(freq/sum(freq),3))

## graph 
trDat_sum %>% ggplot(aes_string(x = target , y = "freq")) + 
  geom_col() +
  labs(title = "Frequency of various site classifications",
       x = "",
       y = "") + 
  coord_flip() +
  theme(axis.text.x = element_text(angle = 90)) 


```


## Data Cleaning 

### Remove covariates with NA values

Input dataframes may have more variables then we are interested in.  This section creates a clean dataframe by limiting it variables listed in the input parameters (i.e., target(s), covariates, transect id, slice id).

```{r set model data frame}
# format data for model by removing covars with NA values
# trDat_all <- trDat[complete.cases(trDat[ , 6:length(trDat)]),]  ### DANGER!!!! specifying covariates by index

# setCols   <- c(target, bgc, groupid, slice, covars) ## list all the columns names: target, bgc, transect id, covars
setCols   <- c(target, groupid, covars) ## list all the columns names: target, bgc, transect id, covars

colNums   <- match(setCols, names(trDat))       ## numerical index
trDat_all <- trDat %>% dplyr::select(colNums)   ## reduces the list to only columns of interest 

```


```{r remove variables with na values, results='hold'}
t <- colSums(is.na(trDat_all)) %>% as.data.frame() %>% rownames_to_column()
names(t) <- c("covar", "na_count") 
t <- t[t$na_count > 0, ] 
t <- t[t$covar %in% covars, ] ## only drop covariates (i.e. not target or tid)

print(paste("The following covariates were removed as they contained NA values:"))
print(t$covar)


## remove covars with NA values 
trDat_all <- trDat_all %>% dplyr::select(-t$covar)
```


### Remove incomplete cases

The data frame may contain incomplete entries -- removed from analysis here.

```{r remove entries with NA values}
# create a subset of data by removing any variables not in model (required for model to run without error)
t <-  trDat_all[!complete.cases(trDat_all), ]
trDat_all <- trDat_all[complete.cases(trDat_all), ]


if (nrow(t) > 0) {
print(paste(nrow(t), "entries were removed from analysis as they were incomplete cases"))
t[, 1:3] %>% knitr::kable(format = "html", caption = "Incomplete cases")
}
```


### Remove low frequecy cases

Further data is removed to ensure cross-fold validation will work.  This is done as a minimum number of samples are needed to allow for the folding of the data. Here there must **50** observations for the cross validated model

```{r}
t <- trDat_sum[trDat_sum$freq > 50,]
flt <- dplyr::pull(t[,1])

dropped <- setdiff(dplyr::pull(trDat_sum[,target]), flt)

print("The following classes were dropped as they did not have enough observations:")
print(dropped)


## adjust training dataframe
trDat_all <-
  trDat_all[trDat_all[[target]] %in% flt,]

```



```{r, eval=FALSE}
## not sure why this is being dropper here -- cc
# trDat <- trDat_all %>%
#     dplyr::select(-c( bgc_cat)) %>%
#     mutate(slice = as.factor(slice))

#trDat <- trDat %>%
#    filter(!is.na(tid))
```


## Set up cross validation 

Original was based on slices and transect_id.  In my mind this is overly complex creating a holdout embeded within a k-fold cross validation .

```{r}
BGC_train <- trDat_all

## Some renaming to facilitate model run
BGC_train <- BGC_train %>% rename(targ = target,    ## rename the target response as 'target'
                                  tid  = groupid)   ## rename the incoming grouping variable as 'tid'

## Convert target and tid to factors
# BGC_train <- BGC_train# %>% 
#   mutate(targ <- as.factor(targ),
#          tid  <- as.factor(tid))
                                  

### Set model recipe 
null_recipe <-
    recipe(targ ~ ., data = BGC_train) %>%
    update_role(tid, new_role = "id variable") # no longer a predictor
                 

### Recipe for Cross validation 
pem_cvfold <- group_vfold_cv(
    BGC_train,
    v = 5,  # number of folds 
    repeats = 5,
    group = tid,
    strata = targ
  )


### Set model engine 
randf_spec <- rand_forest(mtry = 10, min_n = 2, trees = 200) %>%
    set_mode("classification") %>%
    set_engine("ranger", importance = "permutation", verbose = FALSE)


### Assemble modeling process 
pem_workflow <- workflow() %>% 
  add_recipe(null_recipe) %>%
  add_model(randf_spec)

```

## Run the model 

```{r}
if (is.na(rseed)) {
  set.seed(456)
  
} else {
  set.seed(rseed)
  }


cv_results <- fit_resamples(pem_workflow,
                            resamples = pem_cvfold,
                            control = control_resamples(save_pred = TRUE))

  # collect metrics
  cv_metrics <- cv_results  %>% collect_metrics(summarize = FALSE)
  cv_metrics_sum <- cv_results %>% collect_metrics()
  
print(cv_metrics)
print(cv_metrics_sum)
```

## Accuracy metrics 

```{r}
# collect predictions
cv_pred     <- cv_results %>% collect_predictions(summarize = FALSE)
# cv_pred_sum <- cv_results %>% collect_predictions(summarize = TRUE)
# 
# xx <- cv_pred %>% tabyl(targ, .pred_class)
# xy <- xx %>% pivot_longer(cols = !targ,
#                           values_to = "Count",
#                           names_to = "Predicted") 

cfm <- caret::confusionMatrix(cv_pred$.pred_class, cv_pred$targ)
cfm
                       
```


```{r}
PEM_rf1 <- fit(pem_workflow, BGC_train)

final_fit <- pull_workflow_fit(PEM_rf1) # %>%pull(.predictions)
final_fit
oob  <- round(PEM_rf1$fit$fit$fit$prediction.error, 3)



# saveRDS(final_fit, file = paste(paste0(".", outDir), "final_tmodel.rds",sep = "/"))



```


```{r, eval=FALSE}
## More indepth accuracy metrics -- see `acc_metrix()` script bu GP
## not used here 
# 
#   # collect predictions
#   cv_pred <- cv_results %>% collect_predictions(summarize = FALSE)
# 
#   cv_pred_sum <- cv_results %>% collect_predictions(summarize = TRUE)
#   cv_pred_sum <- cv_pred_sum %>% dplyr::select(target, .pred_class)
# 
#   identical(levels(cv_pred_sum$targ),
#             levels(cv_pred_sum$.pred_class))
# 
#   
#   cv_pred_sum %>% 
#     dplyr::select(.pred_class) %>% 
#     group_by(.pred_class) %>% 
#     dplyr::mutate(pred.tot = n()) %>% 
#     ungroup() %>% distinct()
#   
#   
#   ## CV model accuracy metrics
#   cv_pred_sum <- as.data.frame(cv_pred_sum)
# 
#   cv_acc <- acc.metrix(cv_pred_sum) #%>%
#     mutate(slice = k,
#            acc_type = "cv_estimate")
# 
#  ## build final train model and predict test data and compare acc_metrix to cv results
# 
#   PEM_rf1 <- fit(pem_workflow, BGC_train)
# 
#   final_fit <- pull_workflow_fit(PEM_rf1) # %>%pull(.predictions)
# 
#   oob  <- round(PEM_rf1$fit$fit$fit$prediction.error, 3)

```





```{r, eval=FALSE}
## NOTE THIS BLOCK WILL NOT CURRENTLY RUN 

# 
# # Cross validation loop based on slices
# slices <- unique(trDat_all$slice) #%>% droplevels()
# 
# # for all slices
# sresults <- foreach(k = levels(slices)) %do% {
# 
#  # k = levels(slices)[1]
#   ### split into train and test based on 5-site slices
# 
#   # training set
#   BGC_train <- trDat %>% dplyr::filter(!slice %in% k) %>%
#     filter(is.na(target2)) # train only on pure calls
#   BGC_train <- BGC_train %>%
#     dplyr::select(-slice, -target2) %>%
#     droplevels()
# 
#   # test set
#   BGC_test <- trDat %>% filter(slice %in% k)
#   BGC_test_all <- BGC_test # keep for the target2 alt call.
#   BGC_test <- BGC_test %>%
#     dplyr::select(-slice,-target2)
# 
#   ############### Define test recipes and workflow ###################
#   null_recipe <-
#     recipe(target ~ ., data = BGC_train) %>%
#     update_role(tid, new_role = "id variable") # %>%
#     #step_corr(all_numeric()) %>%        # remove correlated covariates
#     #step_dummy(all_nominal(), -all_outcomes()) %>%
#     #step_zv(all_numeric()) #%>%          # remove values with no variance
#     #step_downsample(target, under_ratio = 25) %>%
#    # step_smote(target, over_ratio = 1, neighbors = 2) #%>% #, over_ratio = 1, neighbors = 2) %>%
#     #prep()
# 
#   #summary(null_recipe)
# 
#   if(length(levels(slices))<5) {
#     vv = 5
#   } else {vv = 10}
# 
#   set.seed(345)
#   pem_cvfold <- group_vfold_cv(
#     BGC_train,
#     v = vv,
#     ### need to build a check for number of tids available to automatically reduce this number where necessary # problem with essfmcw
#     repeats = 5,
#     group = tid,
#     strata = target
#   )
# 
#   #summary(pem_cvfold)
# 
#   randf_spec <- rand_forest(mtry = 10, min_n = 2, trees = 200) %>%
#     set_mode("classification") %>%
#     set_engine("ranger", importance = "permutation", verbose = FALSE)
# 
#   ## trees = 200 is approximately good metrics improve by 1% going 100 -> 200 but go down at higher ntrees
# 
#   pem_workflow <- workflow() %>%
#     add_recipe(null_recipe) %>%
#     add_model(randf_spec)
# 
#   #######################################################
# 
#   set.seed(4556)
#   #doParallel::registerDoParallel()
#   # note when smoting with fit_resample you cant use parrallel process or will cause error
# 
#   cv_results <- fit_resamples(pem_workflow,
#                               resamples = pem_cvfold,
#                               control = control_resamples(save_pred = TRUE))
# 
#   # collect metrics
#   cv_metrics <- cv_results  %>% collect_metrics(summarize = FALSE)
#   cv_metrics_sum <- cv_results %>% collect_metrics()
# 
#   # collect predictions
#   cv_pred <- cv_results %>% collect_predictions(summarize = FALSE)
# 
#   cv_pred_sum <- cv_results %>% collect_predictions(summarize = TRUE)
#   cv_pred_sum <- cv_pred_sum %>% dplyr::select(target, .pred_class)
# 
#   identical(levels(cv_pred_sum$target),
#             levels(cv_pred_sum$.pred_class))
# 
#   ## CV model accuracy metrics
#   cv_pred_sum <- as.data.frame(cv_pred_sum)
# 
#   cv_acc <- acc_metrix(cv_pred_sum) %>%
#     mutate(slice = k,
#            acc_type = "cv_estimate")
# 
#  ## build final train model and predict test data and compare acc_metrix to cv results
# 
#   PEM_rf1 <- fit(pem_workflow, BGC_train)
# 
#   final_fit <- pull_workflow_fit(PEM_rf1) # %>%pull(.predictions)
# 
#   oob  <- round(PEM_rf1$fit$fit$fit$prediction.error, 3)
# 
#   ######### Predict Test
#   #test_target <- as.data.frame(BGC_test$target) %>% rename(target = 1)
#   test_target <- BGC_test_all %>% dplyr::select(target, target2)
# 
#   test.pred <-  predict(PEM_rf1, BGC_test)
#   test.pred <- cbind(test_target, test.pred) %>%
#     mutate_if(is.character, as.factor)
#   # levels(train.pred$target)
# 
#   ###harmonize levels
#   targ.lev <- levels(test.pred$target)
#   pred.lev <- levels(test.pred$.pred_class)
#   levs <- c(targ.lev, pred.lev) %>% unique()
#   test.pred$target <- factor(test.pred$target, levels = levs)
#   test.pred$.pred_class <- factor(test.pred$.pred_class, levels = levs)
#   # output test predictions
#   test.pred.out <- test.pred %>% mutate(slice = k)
# 
#   # train.acc <- acc_metrix(train.pred) %>% rename(train = .estimate)
#   test.acc <- acc_metrix(test.pred) %>%
#        mutate(slice = k,
#            acc_type = "test_estimate",
#            oob = oob)
# 
#   ## compare cv stats to test stats
#   acc.compare <- bind_rows(cv_acc, test.acc)
# 
#   return(list(acc.compare, test.pred.out))
# }
# 
# #pem_workflow
# 
# # extract results from sresults
# pred_matrix <- lapply(sresults, function(x) x[[2]])
# acc_results <- lapply(sresults, function(x) x[[1]])
# 
# acc <- as.data.frame(rbindlist(acc_results))
# test.pred <- as.data.frame(rbindlist(pred_matrix))
# 
# save(acc, file = paste(paste0(".", outDir), "model_results.RData", sep = "/"))
# 
# write.csv(acc, file = paste(paste0(".", outDir), "acc_results.csv",sep = "/"))
# 
# 
# # add final model - all output here.
# 
#  ############### Define test recipes and workflow ###################
# 
# final_data <- trDat %>% dplyr::select(-c(tid, target2,slice))
# 
# final_recipe <-
#     recipe(target ~ ., data = final_data) %>%
#     step_downsample(target, under_ratio = 25) %>%
#     step_smote(target, over_ratio = 1, neighbors = 2)
# 
# pem_workflow <- workflow() %>%
#     add_recipe(final_recipe) %>%
#     add_model(randf_spec)
# 
# PEM_final <- fit(pem_workflow, final_data)
# 
# write out model
# saveRDS(PEM_final, file = paste(paste0(".", outDir), "final_tmodel.RDATA",sep = "/"))
# saveRDS(PEM_final, file = paste(paste0(".", outDir), "final_tmodel.rds",sep = "/"))

#acc = read.csv("D:\\PEM_DATA\\BEC_DevExchange_Work\\Deception_AOI\\3_maps_analysis\\models\\forest\\fore_mu_bgc\\64\\SBSmc2\\acc_results.csv")

```


```{r report workflow, include = FALSE}
pem_workflow

```


## Test Accuracy metrics

This table contains a mean and standard deviation of the bootstrapped test metrics.


```{r final test results, include = TRUE, echo = FALSE, eval = FALSE}
## Additional accuracy metrics -- not implemented
# 
# final_metrics <- acc %>%
#   filter(acc_type == "test_estimate") %>%
#   dplyr::select(-acc_type) %>%
#   dplyr::select(accuracy:oob) %>%
#   distinct() %>%
#   pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
#   distinct() %>%
#   group_by(accuracy_type) %>%
#   summarise(mean_val = round(mean(value, na.rm = TRUE),2),
#             st_dev = round(sd(value, na.rm = TRUE),2)) %>%
#   filter(!accuracy_type %in% c("spat_fpa", "spat_pa", "mcc_fpa","mcc_pa"))
# 
# 
# kable(final_metrics, caption = "Average Bootstrapped Test Metrics")
# 
# # confidence interval based on average prediction confus
# 
# conf_matrix <- test.pred %>%
#    conf_mat(target, .pred_class) %>%
#    pluck(1) %>%
#    as_tibble() %>%
#    ggplot(aes(Prediction, Truth, alpha = n)) +
#    geom_tile(show.legend = FALSE) +
#    geom_text(aes(label = n), colour = "black", alpha = 1, size = 3) +
#    theme(axis.text.x = element_text(angle = 90)) +
#    labs(main = "Example Test Confusion Matrix")
# 
#  conf_matrix

```


QUESTION REMAINS: why is the VIP giving 

## Variable importance 

```{r variable importance, include = TRUE, echo = FALSE}
## Recipe: 1. Variable importance plot
vip_recipe <-
    recipe(targ ~ ., data = BGC_train) %>%
    update_role(tid, new_role = "id variable") 

## 2. CV -- Not Applicable


## 3. Model Engine
# 1) basic model all covars
randf_final <- rand_forest(mtry = 20, min_n = 2, trees = 1000) %>%
   set_mode("classification") %>%
   set_engine("ranger", importance = "permutation",
              verbose = TRUE)

## 4. Model workflow

final_vi <- workflow() %>%
   add_recipe(vip_recipe) %>%
   add_model(randf_final) %>%
   fit(BGC_train)
# trDat_final <- trDat %>% dplyr::select(-c(target2, slice))


# BGC_train <- BGC_train %>% mutate(targ = as.factor(targ),
#                      tid  = as.factor(tid))


#%>%
    # step_downsample(target, under_ratio = 25) #%>%
    # step_smote(target, over_ratio = 1, neighbors = 2)

# # calculate the final variable importance per model



 
 
 
 # report final VIP oob - all values
oob_final_vip  <- round(final_vi$fit$fit$fit$prediction.error, 3)
oob_final_vip

final_vi2 <-  final_vi %>%
   pull_workflow_fit() %>%
   vip::vi()

final_vi2
#####
final_vip <-  final_vi %>%
   pull_workflow_fit() %>%
   vip::vip(num_features = 20)
final_vip
```

# COLIN GOT TO HERE ----------

```{r}
## 2) calculate final VIP with uncorrelated variables
## # remove highly correlated variables

descrCor <- cor(BGC_train[,names(BGC_train) %in% covars])
highlyCorDescr <- caret::findCorrelation(descrCor, cutoff = 0.80, verbose = FALSE, names = TRUE)
col.to.rm <- c(highlyCorDescr)

trDat_final = trDat_final %>%
  dplyr::select(names(trDat_final)[!names(trDat_final) %in% col.to.rm])    

vip_recipe <-
    recipe(target ~ ., data = trDat_final) %>%
    update_role(tid, new_role = "id variable") %>%
    step_downsample(target, under_ratio = 25) %>%
    step_smote(target, over_ratio = 1, neighbors = 2)

tic()
final_vip_model <- workflow() %>%
   add_recipe(vip_recipe) %>%
   add_model(randf_final) %>%
   fit(trDat_final) #%>%

 # report final VIP oob
oob_final_vip_uc  <- round(final_vip_model$fit$fit$fit$prediction.error, 3)
oob_final_vip_uc

# plot Vip
final_vip_uc_wf <- final_vip_model %>%
   pull_workflow_fit()

final_vip_uc <- final_vip_uc_wf %>%
   vip(num_feature = 20)

final_vip_uc


# keep top 6 models and compare
vi <- vi(final_vip_uc_wf)
vi <- vi[1:6,1] # remove from 7 onwards

vi <- c("target", "tid", pull(vi))

trDat_final_vip = trDat_final %>%
  dplyr::select(names(trDat_final)[names(trDat_final) %in% vi])    

# fix model and
vip_recipe <-
    recipe(target ~ ., data = trDat_final_vip) %>%
    update_role(tid, new_role = "id variable") %>%
    step_downsample(target, under_ratio = 25) %>%
    step_smote(target, over_ratio = 1, neighbors = 2)

final_six_vip_model <- workflow() %>%
   add_recipe(vip_recipe) %>%
   add_model(randf_final) %>%
   fit(trDat_final_vip)

 # report final VIP oob
oob_six_vip_uc  <- round(final_six_vip_model$fit$fit$fit$prediction.error, 3)
oob_six_vip_uc

# plot Vip
#final_six_vip <- final_six_vip_model  %>%
#   pull_workflow_fit()  %>%
#   vip()

#final_six_vip




```


```{r define models with tuning parameter option, echo = FALSE, eval= FALSE}
# 2: Optional:  Perform model hyperparameter tuning (optional)   

Select model and tune the parameters, note this is time consuming. Model tuning is performed the resampled data by splitting each fold into analysis and assessment components. For each candidate model we should retune the model to select the best fit. However due to the intense computation and time we will tune the model only once for each candidate model and check results with full 10 x 5 CV tuning. Tuning outputs are inspected to assess the best hyperparameters for the given model based on a chosen meaure of accuracy (ie accuracy, j_index, roc). Once the hyperparamters are selected we update the model and apply this to the entire resampled dataset.  Two methods are available



randf_spec <- rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>%
#randf_spec <- rand_forest(mtry = 20, min_n = 2, trees = 1000) %>%
  set_mode("classification") %>%
  set_engine("ranger", importance = "impurity") #or "permutations

# mtry = how many leaves to you sample at each tree
# trees = number of trees, just need enough
# min_n = how many data points need to be in node before stop splitting

pem_workflow <- workflow() %>%
    add_recipe(uni_recipe) %>%
    add_model(randf_spec)

cv_metrics <- metric_set(accuracy, roc_auc, j_index)

set.seed(345)
pem_cvfold <- vfold_cv(trDat,
                          v = 10,
                          repeats = 3,
                          strata = target)


# Two methods are available for tuning; 1) basic grid and 2) regular grid.
# For Random Forest we are using regular grid tune to assess hyperparameters.

# Tune the model
# ##https://www.youtube.com/watch?v=ts5bRZ7pRKQ
# https://www.tidymodels.org/start/case-study/
# http://www.rebeccabarter.com/blog/2020-03-25_machine_learning/
#install.packages("tictoc")

library(tictoc)

# # look at more bound options (ie c(2, 6, 10))
ranger_tune_detail <-
  grid_regular(
    mtry(range = c(2, 40)),
    min_n(range = c(2, 10)),
    levels = 5)

# # re-run the tuning with the explicit parameter sets
tic()
set.seed(4556)
doParallel::registerDoParallel()
ranger_tune <-
  tune_grid(pem_workflow,
            resamples = pem_cvfold,
            #metrics = cv_metrics,
            grid = ranger_tune_detail)
toc()

saveRDS(ranger_tune, file = paste(paste0(".", outDir), "parameter_tune_results.rds", sep = "/"))

# explore ranger tune output
ranger_tune %>%
  dplyr::select(.metrics) %>%
  unnest(cols = c(.metrics))

# explore results of tuning models note different for type of model selected
select_best(ranger_tune, metric = "accuracy")
select_best(ranger_tune, metric = "roc_auc")
#select_best(ranger_tune, metric = "j_index")

autoplot(ranger_tune)

# Plot the impact of different values for the hyperparamters. note these are randomly selected for the number of grids specified (ie. grid = 20).
# This provides an overview of the impact of ech tune paramter. Note this provides an overview as we dont know what min_n was each mtry etc...
# this can be used to set up the tune grid paramter

ranger_tune %>%
  collect_metrics() %>%
  filter(.metric == "roc_auc") %>%
  dplyr::select(mean, min_n, mtry) %>%
  pivot_longer(min_n:mtry,
               values_to = "value",
               names_to = "parameter") %>%
  ggplot(aes(value, mean, colour = parameter)) +
  geom_point(show.legend = FALSE)+
  facet_wrap(~parameter)


# for the 30 m standard pt # minimal change in mtry after 5 - 10
# mtry = 10, min_n = 2

```


## Overall accuracy.

The overall map accuracy was calculated but determining the percent correct for each map unit by comparing transect data (held-out slice).

### Types of accuracy
Several types of accuracy measures were calculated;

1) aspatial: this is equivalent to traditional AA where proportion of map units are compared. Aspatial_acc is the accuracy per slice (i.e total accuracy over the site). Aspatial_meanacc is the accuracy based on the average of map units (ie: 100% correct = 0% correct).

2) spatial (spat_p): this compares spatial equivalents for the primary call for each pixal/point predicted.

3) spatial primary/alt calls (spat_pa). This assigns a value if the alternate call matches the predicted call.

4) fuzzy spatially explicit accuracy: we tested an alternate accuracy measure (spat_fp) to account for calls which were similar (on the edatopic position) to the correct calls. In this case scores could be awarded for on a sliding scale from 1 (Correct) to 0 (no where close) with partial credit assigned to closely related mapunits. Note this requires a matrix which specifies the similarity between all combinations of possible calls. This was also calculated for primary and alternate calls (spat_fpa)


```{r, overall accuracy with confidence intervals, echo = FALSE, eval = TRUE}
bsRes <- acc %>%
    mutate(across(where(is.numeric), ~ replace_na(.,0)))

#write.csv(bsRes, "bsRes_test.csv")

bsRes_all <- bsRes %>%
  group_by(slice, acc_type) %>%

 #mutate(aspat_p = min((targ.ratio/slice_sum),(map.total/trans.total))*100) %>%
  mutate(aspat_p_acc = aspatial_acc,
         aspat_p_meanacc = aspatial_meanacc,
         spat_p_acc = (sum(spat_p)/trans.sum) *100,
         spat_pa_acc = (sum(spat_pa)/trans.sum) *100,
         spat_fp_tot = (sum(spat_fp)/trans.sum) *100,
         spat_fpa_tot = (sum(spat_fpa)/trans.sum) *100,
         spat_pa_mcc = mcc_pa*100,
         spat_fp_mcc = mcc_fp*100,
         spat_fpa_mcc = mcc_fpa*100) %>%

  dplyr::select(c(slice, acc_type, aspat_p_meanacc, aspat_p_acc, spat_p_acc,               spat_pa_acc, spat_fp_tot, spat_fpa_tot,
                  spat_pa_mcc, spat_fp_mcc, spat_fpa_mcc, mcc:recall)) %>%
   pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
  distinct()

p2 <- ggplot(aes(y = value, x = accuracy_type, fill = acc_type), data = bsRes_all) +
   geom_boxplot() +
   scale_fill_brewer(type = "qual") +
   #facet_wrap(~acc_type)+
   #geom_jitter(position=position_jitter(width=.1), colour = "grey", alpha = 0.8) +
   geom_hline(yintercept = 65,linetype ="dashed", color = "red") +
   ggtitle("Overall accuracy measures (median + quartiles)") +
   theme(axis.text.x = element_text(angle = 90)) +
   xlab("Mapunit") + ylab("Accuracy") +
   ylim(-0.05, 100)

p2


bsRes_temp <- bsRes_all %>%
  mutate(type = case_when(
    accuracy_type %in% c("aspat_p_meanacc", "aspat_p_acc") ~ "aspatial",
    accuracy_type %in% c("spat_p_acc","sens", "spec", "precision", "kap") ~ "spatial",
    accuracy_type %in% c("mcc", "f_meas", "precision", "kap") ~ "multi_class",
    accuracy_type %in% c("spat_fp_mcc", "spat_pa_mcc", "spat_fpa_mcc") ~ "fuzzy"
    )) %>%
  filter(!is.na(type)) %>%
  mutate(accuracy_type = ifelse(accuracy_type == "spat_p_acc", "acc_spatial", accuracy_type))


p3 <- ggplot(aes(y = value, x = accuracy_type, fill = acc_type), data = bsRes_temp) +
   geom_boxplot() +
   scale_fill_brewer(type = "qual") +
   facet_grid(~type, scales = "free_x")+
   #geom_jitter(position=position_jitter(width=.1), colour = "grey", alpha = 0.8) +
   geom_hline(yintercept = 65,linetype ="dashed", color = "red") +
   ggtitle("Overall accuracy measures (median + quartiles)") +
   theme(axis.text.x = element_text(angle = 90)) +
   xlab("Mapunit") + ylab("Accuracy") +
   ylim(-0.05, 100)

p3


```


```{r proposed overall metrics, echo = FALSE}

bsRes_limit <- bsRes_all %>%
  filter(acc_type == "test_estimate") %>%
  filter(accuracy_type %in% c("aspat_p_meanacc", "aspat_p_acc", "spat_p_acc",                      "spat_pa_acc","spat_fp_tot" , "spat_fpa_tot", "mcc", "spat_fp_mcc", "spat_pa_mcc", "spat_fpa_mcc"))

bsRes_limit <- bsRes_limit %>%
  mutate(acuracy_type = factor(accuracy_type,
             levels = c("aspat_p_acc","aspat_p_meanacc",
                        "spat_p_acc",  "mcc",
                        "spat_pa_acc", "spat_pa_mcc",
                        "spat_fp_tot" , "spat_fp_mcc",
                        "spat_fpa_tot", "spat_fpa_mcc")))

p2 <- ggplot(aes(y = value, x = accuracy_type, fill = acc_type), data = bsRes_limit) +
   geom_boxplot() +
   scale_fill_brewer(type = "qual") +
   #facet_wrap(~acc_type)+
   #geom_jitter(position=position_jitter(width=.1), colour = "grey", alpha = 0.8) +
   geom_hline(yintercept = 65,linetype ="dashed", color = "red") +
   ggtitle("Proposed accuracy measures (median + quartiles)") +
   theme(axis.text.x = element_text(angle = 90)) +
   xlab("Mapunit") + ylab("Accuracy") +
   ylim(-0.05, 100)

p2

```


## Accuracy per mapunit

We can compare map unit accuracy levels to assess under or acceptable performance per map units.

```{r generate overall mapunit, echo = FALSE, eval = TRUE}

mapunit_tot <- bsRes %>%
  dplyr::filter(acc_type == "test_estimate") %>%
  group_by(slice, target, acc_type) %>%
  dplyr::select(trans.tot, pred.tot, trans.sum, aspat_p, unit_pos, spat_p, spat_fp, spat_pa, spat_fpa, aspatial_acc , aspatial_meanacc)%>%
  rowwise() %>%
  mutate(spat_p_tot = (spat_p/trans.tot) *100,
         spat_pa_tot = (spat_pa/trans.tot) *100,
         spat_fp_tot = (spat_fp/trans.tot)*100,
         spat_fpa_tot = (spat_fpa/trans.tot)*100,
         aspat_p = unit_pos *100) %>%
  dplyr::select(slice, target, spat_p_tot,
                spat_pa_tot, spat_fp_tot, spat_fpa_tot, aspat_p) %>%
  pivot_longer(., cols = where(is.numeric), names_to = "type")


p2 <- ggplot(aes(y = value, x = target, fill = type), data = mapunit_tot) +
   geom_boxplot() +
   #facet_wrap(~acc_type) +
   geom_hline(yintercept = 65,linetype ="dashed", color = "red") +
   ggtitle("Test accuracy per mapunit") +
   theme(axis.text.x = element_text(angle = 90)) +
   xlab("Mapunit") + ylab("Accuracy") +
   ylim(-0.05, 100)

p2


```


# References:
- https://towardsdatascience.com/modelling-with-tidymodels-and-parsnip-bae2c01c131c

* [accuracy](https://yardstick.tidymodels.org/reference/accuracy.html)
* [roc_auc](https://yardstick.tidymodels.org/reference/roc_auc)
* [sensitivity](https://yardstick.tidymodels.org/reference/sens.html)
* [specificity](https://yardstick.tidymodels.org/reference/spec.html)
* [positive predictive value (ppv)](https://yardstick.tidymodels.org/reference/ppv.html)  
